---
title: "SCANN Lab Manual"
author: "Steven M. Weisberg, PhD"
linkcolor: blue
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    includes:
      after_body: after_body.tex
      before_body: before_body.tex
      in_header: preamble.tex
    latex_engine: xelatex
    number_sections: yes
    toc: yes
mainfont: Cambria
fontsize: 12pt
---

```{r setup, include=FALSE}
library("reticulate")
knitr::opts_chunk$set(echo = TRUE)
```

\pagenumbering{gobble}
\newpage
\pagenumbering{arabic} 


# Welcome

Welcome to the [**Spatial Cognition and Navigational Neuroscience**](https://scannlab.psych.ufl.edu) Laboratory at the University of Florida, directed by Steven Weisberg.

Maybe you are just joining the lab or need a refresher on lab policy. Or maybe you're just curious about how we do things. Either way, we're glad you're here! This lab manual is an introduction to how we do work and science in the SCANN lab. The material you find here describes some overarching lab policies, the lab structure, and how to get started.It is also a living document and the manual itself is an introduction to some of the tools you will use when working in the lab (like RStudio, Git, and Slack). 



Our lab manual is open to the public and can be shared under a GNU-3.0 license (the Github repo is [here](https://github.com/scann-lab/lab_manual), but we have also borrowed heavily from others, including [here](https://github.com/ContextLab/lab-manual), [here](https://handbook-public.themusiclab.org/welcome),  [here](https://github.com/alylab/labmanual), and [here](https://github.com/jpeelle/peellelab_manual/). 

You can also find SCANN lab: 

- [On the web](https://scannlab.psych.ufl.edu)
- [On Twitter](https://twitter.com/scannlab)
- [On Github](https://github.com/scann-lab)
- [On Open Science Framework](https://osf.io/4hbgz)^[You will also find our lab wiki here.]


# Bill of Rights and Responsibilities

In the SCANN lab, we practice careful, deliberate, open science. This means that you are 

* **Work with care**. 
* **Our goal is research products**

# Lab Policies, Practices, and Expectations

# Checklist and Signature Page




## Including Code

You can include R code in the document as follows:

### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
